### 2017-10-06 cv-body.tex
Fix typo

\begin{description}
\item[2017]
\textbf{Anderson, S.C.}, E.J. Ward, A.O. Shelton, M.D.\ Adkison, A.H.
Beaudreau, R.E. Brenner, A.C. Haynie, J.C. Shriver, J.T. Watson, B.C.
Williams. Benefits and risks of diversification for individual fishers.
In press at Proceedings of the National Academy of Sciences.
\url{https://doi.org/10.1073/pnas.1702506114} (Open access).
\item[2017]
Hughes, B., S. Lummis, \textbf{S.C. Anderson}, K. Kroeker. Unexpected
resilience of a seagrass system exposed to multiple stressors. Global
Change Biology. In press. \url{https://doi.org/10.1111/gcb.13854}
\item[2017]
Megias, D.A., \textbf{S.C. Anderson}, R.J. Smith, D. Veríssimo.
Investigating the impact of media on demand for wildlife: a case study
of Harry Potter and the UK trade in owls. PLoS ONE. 12(10): e0182368.
\url{https://doi.org/10.1371/journal.pone.0182368} (Open access).
\item[2017]
Chezik, K.A., \textbf{S.C. Anderson}, J.W. Moore. River networks dampen
long-term hydrological signals of climate change. Geophysical Research
Letters. 44(14):7256--7264. \url{https://doi.org/10.1002/2017GL074376}
\item[2017]
Rosenberg, A.A., K.M. Kleisner, J. Afflerbach, \textbf{S.C. Anderson},
M. Dickey-Collas, A.B. Cooper, M.J. Fogarty, E.A. Fulton, N.L.
Gutiérrez, K.J.W. Hyde, E. Jardim, O.P. Jensen, T. Kristiansen, C.
Longo, C.V. Minte-Vera, C. Minto, I. Mosqueira, G.C. Osio, D. Ovando,
E.R. Selig, J.T. Thorson, J.C. Walsh, Y. Ye. Applying a new ensemble
approach to estimating stock status of marine fisheries around the
world. Conservation Letters. In press.
\url{https://doi.org/10.1111/conl.12363}
\item[2017]
\textbf{Anderson, S.C.}, T.A. Branch, A.B. Cooper, N.K. Dulvy.
Black-swan events in animal populations. Proceedings of the National
Academy of Sciences. 114(12): 3252--3257.
\url{https://doi.org/10.1073/pnas.1611525114} (Open access).
\item[2017]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, J. Afflerbach, M. Dickey-Collas, K.M. Kleisner, C.
Longo, G.C. Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig.
Improving estimates of population status and trend with superensemble
models. Fish and Fisheries. 18(4): 732--741.
\url{https://doi.org/10.1111/faf.12200}
\item[2016]
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities.
Proceedings of the Royal Society B: Biological Sciences. 283: 20160816.
\url{https://doi.org/10.1098/rspb.2016.0816}.
\item[2016]
Artelle, K.A., \textbf{S.C. Anderson}, J.D. Reynolds, A.B. Cooper, P.C.
Paquet, C.T. Darimont. Ecology of conflict: marine food supply affects
human-wildlife interactions on land. Scientific Reports. 6: 25936.
\url{https://doi.org/10.1038/srep25936}
(\href{http://www.nature.com/articles/srep25936.pdf}{PDF}).
\item[2016]
Kuriyama, P.T., K. Ono, F. Hurtado-Ferro, A.C. Hicks, I.G. Taylor, R.R.
Licandeo, K.F. Johnson, \textbf{S.C. Anderson}, C.C. Monnahan, M.B.
Rudd, C.C. Stawitz, J.L. Valero. An empirical weight-at-age approach
reduces estimation bias compared to modeling parametric growth in
integrated, statistical stock assessment models when growth is time
varying. Fisheries Research. 180: 119--127.
\url{https://doi.org/10.1016/j.fishres.2015.09.007}
(\href{https://sean.updog.co/papers/Kuriyama_etal_2016_empirical.pdf}{PDF}).

;drop

>>>>

\begin{description}
\tightlist
\item[2017]
\textbf{Anderson, S.C.}, E.J. Ward, A.O. Shelton, M.D.\ Adkison, A.H.
Beaudreau, R.E. Brenner, A.C. Haynie, J.C. Shriver, J.T. Watson, B.C.
Williams. Benefits and risks of diversification for individual fishers.
In press at Proceedings of the National Academy of Sciences.
\url{https://doi.org/10.1073/pnas.1702506114} (Open access).
\item[2017]
Hughes, B., S. Lummis, \textbf{S.C. Anderson}, K. Kroeker. Unexpected
resilience of a seagrass system exposed to multiple stressors. Global
Change Biology. In press. \url{https://doi.org/10.1111/gcb.13854}
\item[2017]
Megias, D.A., \textbf{S.C. Anderson}, R.J. Smith, D. Veríssimo.
Investigating the impact of media on demand for wildlife: a case study
of Harry Potter and the UK trade in owls. PLoS ONE. 12(10): e0182368.
\url{https://doi.org/10.1371/journal.pone.0182368} (Open access).
\item[2017]
Chezik, K.A., \textbf{S.C. Anderson}, J.W. Moore. River networks dampen
long-term hydrological signals of climate change. Geophysical Research
Letters. 44(14):7256--7264. \url{https://doi.org/10.1002/2017GL074376}
\item[2017]
Rosenberg, A.A., K.M. Kleisner, J. Afflerbach, \textbf{S.C. Anderson},
M. Dickey-Collas, A.B. Cooper, M.J. Fogarty, E.A. Fulton, N.L.
Gutiérrez, K.J.W. Hyde, E. Jardim, O.P. Jensen, T. Kristiansen, C.
Longo, C.V. Minte-Vera, C. Minto, I. Mosqueira, G.C. Osio, D. Ovando,
E.R. Selig, J.T. Thorson, J.C. Walsh, Y. Ye. Applying a new ensemble
approach to estimating stock status of marine fisheries around the
world. Conservation Letters. In press.
\url{https://doi.org/10.1111/conl.12363}
\item[2017]
\textbf{Anderson, S.C.}, T.A. Branch, A.B. Cooper, N.K. Dulvy.
Black-swan events in animal populations. Proceedings of the National
Academy of Sciences. 114(12): 3252--3257.
\url{https://doi.org/10.1073/pnas.1611525114} (Open access).
\item[2017]
\textbf{Anderson, S.C.}, A.B. Cooper, O.P. Jensen, C. Minto, J.T.
Thorson, J.C. Walsh, J. Afflerbach, M. Dickey-Collas, K.M. Kleisner, C.
Longo, G.C. Osio, D. Ovando, I. Mosqueira, A.A. Rosenberg, E.R. Selig.
Improving estimates of population status and trend with superensemble
models. Fish and Fisheries. 18(4): 732--741.
\url{https://doi.org/10.1111/faf.12200}
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities.
Proceedings of the Royal Society B: Biological Sciences. 283: 20160816.
\url{https://doi.org/10.1098/rspb.2016.0816}.
Artelle, K.A., \textbf{S.C. Anderson}, J.D. Reynolds, A.B. Cooper, P.C.
Paquet, C.T. Darimont. Ecology of conflict: marine food supply affects
human-wildlife interactions on land. Scientific Reports. 6: 25936.
\url{https://doi.org/10.1038/srep25936}
(\href{http://www.nature.com/articles/srep25936.pdf}{PDF}).
Kuriyama, P.T., K. Ono, F. Hurtado-Ferro, A.C. Hicks, I.G. Taylor, R.R.
Licandeo, K.F. Johnson, \textbf{S.C. Anderson}, C.C. Monnahan, M.B.
Rudd, C.C. Stawitz, J.L. Valero. An empirical weight-at-age approach
reduces estimation bias compared to modeling parametric growth in
integrated, statistical stock assessment models when growth is time
varying. Fisheries Research. 180: 119--127.
\url{https://doi.org/10.1016/j.fishres.2015.09.007}
(\href{https://sean.updog.co/papers/Kuriyama_etal_2016_empirical.pdf}{PDF}).
